Clicks and Cliques

### 2019-01-02 papersoul.Rnw
typo
add shape aes in fig 6

census.data %>%
   mutate(cl.2 = cutree(hc2, 4) ) %>%
     select(aveageF, prop1821, un.rate, Bachelor.s.degree.or.higher., gini , own.rate ,  prop.new.entry, afri.prop, prop.no.workers, cl.2) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  ungroup() %>%
  rename(Age.Fem = aveageF, Yr.1821 = prop1821, Unemp = un.rate, Bachelor = Bachelor.s.degree.or.higher., Gini = gini, Own.rate = own.rate, New.entry = prop.new.entry, Afri.pr= afri.prop, No.workers = prop.no.workers, cl.2 = cl.2) %>% 
  mutate(cl.2 = factor(cl.2)) %>%
  ggparcoord(columns = 2:10, scale = 'std',
             groupColumn = 'cl.2', showPoints = T, 
             order = c(3, 5, 6, 8, 2, 4, 10, 7, 9))  + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  labs(x = '', y = '') + 
  scale_color_brewer(type = 'qual', palette = 2, name = 'Group')

>>>>

census.data %>%
  mutate(cl.2 = cutree(hc2, 4) ) %>%
  select(aveageF, prop1821, un.rate, Bachelor.s.degree.or.higher., gini , own.rate ,  prop.new.entry, afri.prop, prop.no.workers, cl.2) %>% 
  group_by(cl.2) %>%
  summarise_all(funs(mean)) %>%
  ungroup() %>%
  rename(Age.Fem = aveageF, Yr.1821 = prop1821, Unemp = un.rate, Bachelor = Bachelor.s.degree.or.higher., Gini = gini, Own.rate = own.rate, New.entry = prop.new.entry, Afri.pr= afri.prop, No.workers = prop.no.workers, cl.2 = cl.2) %>% 
  mutate(cl.2 = factor(cl.2)) %>%
  gather(var, val, -cl.2) %>% 
  group_by(var) %>% 
  mutate(mm = mean(val), ss = sd(val) ) %>% 
  ungroup() %>% 
  mutate(val.st = (val-mm)/ss, 
         var.or = fct_relevel(var, c('Yr.1821', 'Bachelor', 'Gini', 'New.entry',
                                     'Age.Fem', 'Unemp', 'No.workers', 'Own.rate',
                                     'Afri.pr')) ) %>% 
  ggplot( aes(x=var.or, y=val.st, color = cl.2, shape=cl.2, group=cl.2) ) + 
  geom_point(size = I(3)) + geom_line() + 
  theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
  labs(x = '', y = '', color = 'Group', shape = 'Group') + 
  scale_color_brewer(type = 'qual', palette = 'Dark2')

# census.data %>%
#    mutate(cl.2 = cutree(hc2, 4) ) %>%
#      select(aveageF, prop1821, un.rate, Bachelor.s.degree.or.higher., gini , own.rate ,  prop.new.entry, afri.prop, prop.no.workers, cl.2) %>% 
#   group_by(cl.2) %>%
#   summarise_all(funs(mean)) %>%
#   ungroup() %>%
#   rename(Age.Fem = aveageF, Yr.1821 = prop1821, Unemp = un.rate, Bachelor = Bachelor.s.degree.or.higher., Gini = gini, Own.rate = own.rate, New.entry = prop.new.entry, Afri.pr= afri.prop, No.workers = prop.no.workers, cl.2 = cl.2) %>% 
#   mutate(cl.2 = factor(cl.2)) %>%
#   ggparcoord(columns = 2:10, scale = 'std',
#              groupColumn = 'cl.2', showPoints = T, 
#              order = c(3, 5, 6, 8, 2, 4, 10, 7, 9),
#              aes(shape = cl.2))  + 
#   theme(axis.text.x = element_text(angle = 90, size = I(15))) + 
#   labs(x = '', y = '') + 
#   scale_color_brewer(type = 'qual', palette = 2, name = 'Group')
